Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Cleaned up plotting code

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

collap_types_count_barplot <- collab_types_count %>%
    ggplot() + geom_bar(aes(x = reorder(author_affiliation_type, n),
                            y = n
                            ),
                        stat = 'identity',
                        color = 'black'
                        ) +
    scale_y_continuous(breaks = seq(0, 140, 20),
                       labels = seq(0, 140, 20)
                       ) +
    labs(title = 'Number of studies per collaboration type', 
         x = '', 
         y = 'Number of studies') + 
  coord_flip() +
  theme_minimal() +
  theme(legend.position = 'none')

>>>>

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
collap_types_count_barplot <- ggplot(data = collab_types_count) + 
  geom_bar(aes(x = reorder(author_affiliation_type, n), y = n),
           stat = 'identity',
           color = 'black') +
    scale_y_continuous(breaks = seq(0, 140, 20),
                       labels = seq(0, 140, 20)
                       ) + 
    labs(title = 'Number of studies per collaboration type', 
         x = ' ', 
         y = 'Number of studies') + 
  coord_flip() +
  theme_minimal() +
  theme(legend.position = 'none')
